---
title: "Estimates from Polymod Data"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(socialmixr)
library(dplyr)
```

## Modelling the probability of a within household contact

```{r}
data(polymod)
```

```{r}
contacts = polymod$contacts
participants = polymod$participants
```

```{r}
# Join the participant data frame to the dataframe that stores contact data on the participant ID and filter to the United Kingdom
uk_data = participants %>%
  filter(country == "United Kingdom") %>%
  left_join(contacts, by = "part_id")# %>%
  #select(part_id, hh_size, cnt_home, frequency_multi)
```

We filter contacts down to those whom the age of the contact matches the contact of someone within the household.

```{r}
within_household_contacts = uk_data %>%
  filter(cnt_home == 1 & # within household contacts must occur at home
        frequency_multi == 1) %>% # contacts must be daily or weekly)
  filter(
    cnt_age_exact == hh_age_1 |
    cnt_age_exact == hh_age_2 |
    cnt_age_exact == hh_age_3 |
    cnt_age_exact == hh_age_4 |
    cnt_age_exact == hh_age_5 |
    cnt_age_exact == hh_age_6)

```

Therefore, we know how many contacts ocurred to other members of the household.

We need to know how many households of each size there were, then we are able to work out the probability of contacting a household member for each of the household sizes.

```{r}
number_houses_uk = participants %>%
  filter(country == "United Kingdom") %>%
  select(hh_size) %>%
  group_by(hh_size) %>%
  summarise(number_households = n())

```

```{r}
contacts_house_size = number_houses_uk %>%
  left_join(within_household_contacts, "hh_size") %>%
  group_by(hh_size) %>%
  summarise(number_contacts = n())
contacts_house_size
```
```{r}
hh_summary = number_houses_uk %>%
  left_join(contacts_house_size) %>%
  mutate(contact_prob = number_contacts / ((hh_size - 1)*number_households ))
hh_summary
```

total_contact_means = [7.238, 10.133, 11.419, 12.844, 14.535, 15.844], see "Polymod Estimates - HH_sizes.Rmd".

## Setting the the contact types:

```{r}

# We assign the local and global tags
uk_data = uk_data %>%
  # a contact is global if it occurs at home daily
  mutate(local =
    (cnt_home == 1 &
     frequency_multi == 1) & 
    # the age of a contact must match the age of another hh member
    (cnt_age_exact == hh_age_1 |
    cnt_age_exact == hh_age_2 |
    cnt_age_exact == hh_age_3 |
    cnt_age_exact == hh_age_4 |
    cnt_age_exact == hh_age_5 |
    cnt_age_exact == hh_age_6))
```

Assigning contact labels

```{r}
uk_data_contacts = uk_data %>%
  mutate(local =
    (cnt_home == 1 &
     frequency_multi == 1) & 
    # the age of a contact must match the age of another hh member
    (cnt_age_exact == hh_age_1 |
    cnt_age_exact == hh_age_2 |
    cnt_age_exact == hh_age_3 |
    cnt_age_exact == hh_age_4 |
    cnt_age_exact == hh_age_5 |
    cnt_age_exact == hh_age_6)) %>%
  mutate(
    work_travel =(cnt_work == 1 |cnt_transport == 1) & !local
    ) %>%
  mutate(
    school = (cnt_school == 1 & !local)
    ) %>%
  mutate(
    leisure = (cnt_leisure == 1 & !local)
    ) %>%
  mutate(
    other = (cnt_otherplace == 1 & !local & !leisure)
    ) %>%
  left_join(number_houses_uk) %>%
  group_by(hh_size) %>%
  filter(!is.na(local) & !is.na(work_travel) & !is.na(school) & !is.na(leisure) & !is.na(other))
```

```{r}
pre_lockdown_means = uk_data_contacts %>%
  group_by(hh_size) %>%
  summarise(
    all=sum((local+work_travel+school+leisure+other)/number_households),
    local = sum(local/number_households),
    global = all - local,
    work_travel = sum(work_travel/number_households),
    school=sum(school/number_households),
    leisure=sum(leisure/number_households),
    other=sum(other/number_households))
```

```{r}
post_lockdown_means = contact_means_hh_size %>%
  group_by(hh_size) %>%
  filter(week != 6) %>%
  summarize(
    all = mean(mean_all),
    local = mean(mean_hh),
    global = mean(mean_not_hh),
    work = mean(mean_work),
    school = mean(mean_school),
    home = mean(mean_home),
    not_home = mean(mean_not_home))

# Get the mean difference vectors

```


```{r}
delta_school = pre_lockdown_means$school[1:6] - post_lockdown_means$school[1:6]
delta_work = pre_lockdown_means$work_travel[1:6] - post_lockdown_means$work[1:6]
delta_leisure = pre_lockdown_means$leisure[1:6]
```

```{r}
lockdown_global_contact_reduction = 1 - post_lockdown_means$global[1:6] / pre_lockdown_means$global[1:6]
lockdown_global_contact_reduction
```

```{r}
lockdown_global_contact_reduction = 1 - post_lockdown_means$global[1:6] / pre_lockdown_means$global[1:6]
lockdown_global_contact_reduction

```

## TOTALLY ARBITRARY SCENARIO A:

```{r}
scenario_A = 1 - (post_lockdown_means$global[1:6] + 0.2*post_lockdown_means$work[1:6] + 0.1*delta_school)/ pre_lockdown_means$global[1:6]
scenario_A
```

## Scenario B:

```{r}
scenario_B = 1 - (post_lockdown_means$global[1:6] + 0.3*post_lockdown_means$work[1:6] + 0.25*delta_school + 0.1*delta_leisure)/ pre_lockdown_means$global[1:6]
scenario_B
```

## Scenario C:

```{r}
scenario_C = 1 - (post_lockdown_means$global[1:6] + 0.3*post_lockdown_means$work[1:6] + 0.5*delta_school + 0.1*delta_leisure)/ pre_lockdown_means$global[1:6]
scenario_C
```


## Scenario D:

```{r}
scenario_D = 1 - (post_lockdown_means$global[1:6] + 0.4*post_lockdown_means$work[1:6] + 0.6*delta_school + 0.3*delta_leisure)/ pre_lockdown_means$global[1:6]
scenario_D
```

```{r}
scenario_E = 1 - (post_lockdown_means$global[1:6] + 0.5*post_lockdown_means$work[1:6] + delta_school + 0.75*delta_leisure)/ pre_lockdown_means$global[1:6]
scenario_E
```

## Scenario E:


```{r}
A=round(scenario_A, 3)
B=round(scenario_B, 3)
C=round(scenario_C, 3)
D=round(scenario_D, 3)
E=round(scenario_E, 3)

rbind(append("A", A),
append("B", B),
append("C", C),
append("D", D),
append("E", E))
```


By household size.

```{r}
summary = model_data_no_multiple %>%
#  group_by(hh_size) %>%
  filter(!is.na(cnt_home)) %>%
  summarize(prop_within_house = mean(cnt_home), n = n())
summary
prop_within_house <- as.numeric(unlist(summary[1]))
```



```{r}
uk_data
```



```{r}
uk_data %>%
  filter(!is.na(local)) %>%
  group_by(hh_size) %>%
  summarise(sum(local), sum(!local))
```


Prop work contacts

```{r}
summary = uk_data %>%
#  group_by(hh_size) %>%
  filter(!is.na(cnt_work)) %>%
  summarize(prop_work = mean(cnt_work), n = n())
prop_work <- unlist(as.numeric(summary[1]))

summary = uk_data %>%
 group_by(part_id) %>%
  filter(!is.na(cnt_work)) %>%
  summarize(sum_work = sum(cnt_work), n = n())
mean.work <-mean(as.numeric(unlist(summary[2])))
```
 
 Transport (add in to work)

```{r}
summary = uk_data %>%
#  group_by(hh_size) %>%
  filter(!is.na(cnt_transport)) %>%
  summarize(prop_transport = mean(cnt_transport), n = n())
summary
prop_transport <- unlist(as.numeric(summary[1]))

summary = uk_data %>%
 group_by(part_id) %>%
  filter(!is.na(cnt_transport)) %>%
  summarize(sum_transport = sum(cnt_transport), n = n())
mean.transport <-mean(as.numeric(unlist(summary[2])))
```


By household, prop school contacts.

```{r}
summary = uk_data %>%
#  group_by(hh_size) %>%
  filter(!is.na(cnt_school)) %>%
  summarize(prop_school = mean(cnt_school), n = n())
summary[1]
prop_school <- unlist(as.numeric(summary[1]))

summary = uk_data %>%
 group_by(part_id) %>%
  filter(!is.na(cnt_school)) %>%
  summarize(sum_school = sum(cnt_school), n = n())
mean.school <-mean(as.numeric(unlist(summary[2])))
```


```{r}
summary = uk_data %>%
# group_by(hh_size) %>%
  filter(!is.na(cnt_leisure)) %>%
  summarize(prop_leisure = mean(cnt_leisure), n = n())
prop_leisure <- unlist(as.numeric(summary[1]))

summary = uk_data %>%
 group_by(part_id) %>%
  filter(!is.na(cnt_leisure)) %>%
  summarize(sum_leisure = sum(cnt_leisure), n = n())
mean.leisure <-mean(as.numeric(unlist(summary[2])))
```

```{r}
# Creating the name vector
types <- c("work_travel","school","leisure")
poly_prop <- c((prop_work+prop_transport), prop_school, prop_leisure)
pop <- poly_prop/(1-prop_within_house)
poly_num <- c((mean.work+mean.transport),mean.school, mean.leisure)
red_num <- 0.2*poly_num
num_now <- c(0.6,0,0)
current <- c(0.5,0,0)*pop
may <- c((1.2*num_now[1]), 0.11*poly_num[2], 0*poly_num[3])
jun <- c((1.2*1.1*num_now[1]), 0.25*poly_num[2], 0.1*poly_num[3])
jul <- c((1.2*1.1^2*num_now[1]), 0.60*poly_num[2], 0.3*poly_num[3])
aug <- c((1.2*1.1^3*num_now[1]), 1*poly_num[2], 0.75*poly_num[3])

# These give projected NUMBERS of contacts for each scenario month by type
## (Gave up trying to work entirely with proportions, so working woth mean numbers of contacts instead)
## Had to assume 10% of usual (ie polymod) leisure compared to now because we are assuming leisure is currently 0
## Looks like about 0.6 work contacts right now person according to CoMix
scen1 <- cbind.data.frame(types, poly_num, red_num, num_now, poly_prop, pop, current, may, jun, jul, aug)

jun2 <- c((1.2*1.1*num_now[1]), 0.5*poly_num[2], 0.1*poly_num[3])

scen2 <- cbind.data.frame(types, poly_num, red_num, num_now, poly_prop, pop, current, may, jun2, jul, aug)

#Numbers of outside contacts per type

adults1 <- cbind(may[-2], jun[-2], jul[-2], aug[-2])
chil1 <- cbind(may[-1], jun[-1], jul[-1], aug[-1])
tot.adult1 <- colSums(adults1)
tot.chil1 <- colSums(chil1)

adults2 <- cbind(may[-2], jun2[-2], jul[-2], aug[-2])
chil2 <- cbind(may[-1], jun2[-1], jul[-1], aug[-1])
tot.adult2 <- colSums(adults2)
tot.chil2 <- colSums(chil2)

hh1.1 <- tot.adult1
hh2.1 <- 2*tot.adult1
hh3.1 <- hh2.1+tot.chil1
hh4.1 <- hh3.1+tot.chil1
hh5.1 <- hh4.1+tot.chil1
hh6.1 <- hh5.1+tot.chil1

scen1.contacts<- data.frame(matrix(as.numeric(unlist(rbind(hh1.1, hh2.1, hh3.1, hh4.1, hh5.1, hh6.1))), ncol=4))
colnames(scen1.contacts) <- c("may", "jun", "jul", "aug")
rownames(scen1.contacts) <- c("hh1", "hh2", "hh3", "hh4", "hh5", "hh6")

hh1.2 <- tot.adult2
hh2.2 <- 2*tot.adult2
hh3.2 <- hh2.2+tot.chil2
hh4.2 <- hh3.2+tot.chil2
hh5.2 <- hh4.2+tot.chil2
hh6.2 <- hh5.2+tot.chil2

scen2.contacts<- data.frame(matrix(as.numeric(unlist(rbind(hh1.2, hh2.2, hh3.2, hh4.2, hh5.2, hh6.2))), ncol=4))
colnames(scen2.contacts) <- c("may", "jun", "jul", "aug")
rownames(scen2.contacts) <- c("hh1", "hh2", "hh3", "hh4", "hh5", "hh6")

write.csv(scen1.contacts,"Data/scen1_mean_contacts.csv", row.names = T)

write.csv(scen2.contacts,"Data/scen2_mean_contacts.csv", row.names = T)



```